Depletion capabilities in the OpenMC Monte Carlo particle transport code

### 2020-07-13 manuscript.tex
More suggested changes from @cjosey

More sophisticated predictor--corrector methods have been introduced by
\citet{isotalo2011ane2,isotalo2011ane3}. In the CE/LI (constant extrapolation,
linear interpolation) method, the end-of-step composition is first predicted
using $\vect{A}(\vect{n}_i)$:
\begin{equation}
  \vect{n}_{i+1}^p = \exp \left( h\vect{A}(\vect{n}_i) \right) \vect{n}_i.
\end{equation}
Then, $\vect{n}_{i+1}^p$ is used to reevaluate $\vect{A}$. An approximation of
$\vect{A}$ that depends on time is formed by linearly interpolating between
$\vect{A}(\vect{n}_i)$ and $\vect{A}\left(\vect{n}_{i+1}^p\right)$.
\Cref{eq:depletion-matrix} thus becomes
\begin{equation}
  \label{eq:linear-ode}
  \frac{d\vect{n}}{dt} = \hat{\vect{A}}(t) \vect{n}
\end{equation}
where
\begin{equation}
  \label{eq:linear-interp}
  \hat{\vect{A}}(t) = \left ( 1 - \frac{t}{h} \right) \vect{A}(\vect{n}_i) +
  \frac{t}{h} \vect{A}\left(\vect{n}_{i+1}^p \right).
\end{equation}
We see that $\hat{\vect{A}}$ no longer depends on $\vect{n}$ thereby making
\cref{eq:linear-ode} a linear nonautonomous ODE. Because $\hat{\vect{A}}$ is a
function of time, an approximation is still needed to obtain $\vect{n}_{i+1}$.
The simplest approach~\citep{isotalo2011ane2} is to average
\cref{eq:linear-interp} over the step,
\begin{equation}
  \bar{\vect{A}} = \int_0^h dt \, \hat{\vect{A}}(t) = \frac{\vect{A}(\vect{n}_i)
  + \vect{A}(\vect{n}_{i+1}^p)}{2},
\end{equation}
and then use $\bar{\vect{A}}$ to deplete over the full step:
\begin{equation}
  \vect{n}_{i+1} = \exp \left ( h \bar{\vect{A}} \right ) \vect{n}_i.
\end{equation}
\citet{isotalo2011ane3} suggested an improvement over this approach wherein
$\hat{\vect{A}}$ is averaged over substeps instead of the entire interval. That
is, if we divide the timestep into $m$ substeps, the solution is given by
\begin{equation}
  \begin{split}
    \label{eq:celi-substeps}
    \vect{A}_s &= \int_{(s-1)h/m}^{sh/m} dt \; \hat{\vect{A}}(t), \quad s=1,\dots,m \\
    \vect{n}_{i+1} &= \exp\left(\vect{A}_m \right) \exp \left(\vect{A}_{m-1}\right)
    \cdots \exp\left(\vect{A}_1\right) \vect{n}_i.
  \end{split}
\end{equation}
While using substeps is a reasonable approach for solving \cref{eq:linear-ode},
there are other methods as well. For example, some codes use a backward
differentiation formula rather than a method based on an exponential
integrator~\citep{carpenter2009mc,hykes2017mc,sublet2017nds}.

@@

\Cref{fig:pwr-keff} shows the difference between $k_\text{eff}$ calculated by
OpenMC and Serpent. The blue points correspond to results using the full
depletion chain, the red points correspond to points using the reduced chain,
and the green points correspond to results using the CASL chain. For each chain,
the use of interpolated FPYs is denoted by circles and thermal FPYs by x's. At
zero days, the difference in $k_\text{eff}$ between OpenMC and Serpent is not
statistically significant. As the burnup increases, the difference for the full
chain cases rises to about 20 pcm. The reduced chain case exhibits the exact
same behavior as the full chain as one would expect. Use of the CASL chain
results in a slightly larger difference between OpenMC and Serpent at 50 MWd/kg,
about 40 pcm. We also see that for both the full and CASL chains, changing the
method for handling FPY energy dependence doesn't appear to have much of an
effect on $k_\text{eff}$, which is primarily driven by the prediction of
actinide concentrations.
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr_keff.pdf}
  \caption{Difference in the effective multiplication factor, $k_\text{eff}$,
  between OpenMC and Serpent for the PWR pincell model. While not shown, the one
  standard deviation uncertainty in the difference is about 3.5 pcm.}
  \label{fig:pwr-keff}
\end{figure}

@@

The predicted concentration of fission products depends on both the depletion
chain that is used and the method for handling the energy dependence of the FPY.
We begin with results for the full depletion chain and interpolated FPYs, which
most closely matches the method used in Serpent; \cref{fig:pwr-fp-full-average}
shows the relative difference in fission product concentrations between OpenMC
and Serpent for this case. Most of the differences are less than 0.2\%, and only
a few fission products show differences up to 0.5\%.
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr_fp_full_average.pdf}
  \caption{Relative difference in fission product concentrations between OpenMC
  and Serpent for the PWR pincell model at 5, 12.5, 30, and 50 MWd/kg using the
  full depletion chain and interpolated FPYs.}
  \label{fig:pwr-fp-full-average}
\end{figure}

\Cref{fig:pwr-fp-full-thermal} shows the predicted fission product concentrations
when using the full depletion chain along with thermal FPYs. In this case,
although most fission products are within 1\% of Serpent, they are
systematically overpredicted other than a few nuclides. Because Serpent uses the
average fission energy to interpolate between two sets of FPYs, the systematic
difference is expected when using thermal FPYs in OpenMC. As the incident energy
of a neutron causing fission increases, the ``saddle'' and ``wings'' in the FPY
curve tend to increase significantly, and the peaks around $A=95$ and $A=135$
tend to slightly decrease. This corresponds to exactly what is observed in
\cref{fig:pwr-fp-full-thermal}. Because thermal FPYs were used in OpenMC for
this case, we expect that fission products near one of the two peaks of the FPY
curve will be slightly overpredicted relative to Serpent, and fission products
away from the peak will be underpredicted. This can be confirmed for particular
nuclides. Take, for example, $^{109}$Ag; in the $A=109$ mass chain, the nuclides
with the highest independent yields are $^{109}$Tc and $^{109}$Mo. Both these
nuclides have independent yields that increase significantly with increasing
neutron energy. The same situation occurs for $^{129}$I, whose predominant
precursor is $^{129}$Sn. The independent yields for these three precursor
nuclides are shown in \cref{tab:fp-yields}.
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr_fp_full_thermal.pdf}
  \caption{Relative difference in fission product concentrations between OpenMC
  and Serpent for the PWR pincell model at 5, 12.5, 30, and 50 MWd/kg using the
  full depletion chain and thermal FPYs.}
  \label{fig:pwr-fp-full-thermal}
\end{figure}
\begin{table}[htbp]
  \centering
  \caption{Independent yields of select fission products due to fission in
  $^{235}$U (data from the ENDF/B-VII.1 FPY sublibrary).}
  \label{tab:fp-yields}
  \begin{tabular}{cccc}
    \toprule
    \textbf{Energy Spectrum} & \textbf{$^{109}$Tc} & \textbf{$^{109}$Mo} & \textbf{$^{129}$Sn} \\
    \midrule
    Thermal & 0.00013 & 0.00015 & 0.00230 \\
    Fast & 0.00034 & 0.00042 & 0.00550 \\
    Fusion & 0.00598 & 0.00109 & 0.01162 \\
    \bottomrule
  \end{tabular}
\end{table}

\Cref{fig:pwr-fp-casl-average} shows the relative difference in predicted
fission product concentrations between OpenMC and Serpent when using the CASL
depletion chain and interpolated FPYs. As in \cref{fig:pwr-fp-full-average},
almost all fission products are predicted to well within 1\% at 50 MWd/kg.
However, in this case there is one clear outlier: $^{85}$Kr. Upon further
investigation, it was determined that the root cause for this difference is the
fact that the CASL depletion chain uses a cumulative yield for $^{85}$Kr, and
the cumulative yield of $^{85}$Kr is known to be inconsistent with the
independent yields of the $A=85$ mass chain in
ENDF/B-VII.1~\citep{pigni2015nds}. Serpent relies solely on independent yields
in its depletion solver (as does the full depletion chain). We can conclude,
then, that there is nothing inherently wrong with the CASL depletion chain or
OpenMC; it is simply a matter of the underlying nuclear data being inconsistent.
The 5\% underprediction of $^{85}$Kr is also likely responsible for the slightly
higher difference in $k_\text{eff}$ for the CASL depletion chain shown in
\cref{fig:pwr-keff}.
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr_fp_casl_average.pdf}
  \caption{Relative difference in fission product concentrations between OpenMC
  and Serpent for the PWR pincell model at 5, 12.5, 30, and 50 MWd/kg using the
  CASL depletion chain and interpolated FPYs.}
  \label{fig:pwr-fp-casl-average}
\end{figure}

\Cref{fig:pwr-fp-casl-thermal} shows the relative difference in predicted in
fission product concentrations when using the CASL depletion chain along with
thermal FPYs. The results are quite close to those shown
\cref{fig:pwr-fp-full-thermal}, with the exception of $^{85}$Kr for the
aforementioned reasons.
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr_fp_casl_thermal.pdf}
  \caption{Relative difference in fission product concentrations between OpenMC
  and Serpent for the PWR pincell model at 5, 12.5, 30, and 50 MWd/kg using the
  CASL depletion chain and thermal FPYs.}
  \label{fig:pwr-fp-casl-thermal}
\end{figure}

@@

\Cref{fig:sfr-keff} shows the difference between $k_\text{eff}$ calculated by
OpenMC and Serpent as the assembly is depleted. The blue points correspond to
results using the full depletion chain, and the green points correspond to
results using the CASL chain. For each chain, simulations with probability
tables on are denoted by circles and simulations without probability tables are
denoted by squares. Unlike in the PWR pincell case, there is a statistically
significant difference in $k_\text{eff}$ at zero days. Let us first consider the
case with probability tables turned off. In this case, $k_\text{eff}$ calculated
by OpenMC is about 20 pcm higher than that of Serpent. When using the full
depletion chain, there is no change in the difference between OpenMC and Serpent
with increasing burnup. When using the CASL depletion chain, the difference
increases by about 20--30 pcm, similar to the behavior shown in
\cref{fig:pwr-keff}. With probability tables turned on, however, the situation
is quite different. At zero days, $k_\text{eff}$ calculated by OpenMC is 20 pcm
lower than the value calculated by Serpent. As the burnup increases, there is an
increasing positive bias between OpenMC and Serpent. To understand the cause of
this difference, it is instructive to look at differences in isotopic
compositions.
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/sfr_keff.pdf}
  \caption{Difference in the effective multiplication factor, $k_\text{eff}$,
  between OpenMC and Serpent for the SFR assembly model. While not shown, the one
  standard deviation uncertainty in the difference is about 3.5 pcm.}
  \label{fig:sfr-keff}
\end{figure}

@@

When comparing results on the SFR assembly model, larger differences in
$k_\text{eff}$ and isotopic concentrations were observed when unresolved
resonance region probability tables were turned on. These differences were found
to be related to how the temperature dependence of cross sections is treated in
the unresolved resonance region. In OpenMC, when the temperature of a material
is between two temperatures at which probability tables are tabulated,
statistical interpolation between the tables is performed. Serpent, on the other
hand, uses probability tables at the lower tabulated temperature. For the SFR
model, this results in lower parasitic neutron absorption in $^{238}$U, lower
production of $^{239}$Pu, and ultimately a lower $k_\text{eff}$. After depleting
for 360 days, there was a 100 pcm difference between OpenMC and Serpent due to
this effect. Although this is not a huge difference, users who are simulating
problems with a non-uniform temperature distribution should be aware of this
behavior.

@@

While the focus in this work has primarily been on correctness and accuracy, the
performance of a coupled transport--depletion simulation is also an important
consideration that directly impacts usability. The need to determine reaction
rates for hundreds of nuclides leads to a significant performance degredation
during a transport simulation. Research on methods to reduce the computational
expense of obtaining transmutation reaction rates~\cite{salcedoperez2019mc} show
promise but have yet to be incorporated in a release of OpenMC.

>>>>

More sophisticated predictor--corrector methods have been introduced by
\citet{isotalo2011ane2,isotalo2011ane3}. In the CE/LI (constant extrapolation,
linear interpolation) method, the end-of-step composition is first predicted
using $\vect{A}(\vect{n}_i)$:
\begin{equation}
  \vect{n}_{i+1}^p = \exp \left( h\vect{A}(\vect{n}_i) \right) \vect{n}_i.
\end{equation}
Then, $\vect{n}_{i+1}^p$ is used to reevaluate $\vect{A}$. An approximation of
$\vect{A}$ that depends on time is formed by linearly interpolating between
$\vect{A}(\vect{n}_i)$ and $\vect{A}\left(\vect{n}_{i+1}^p\right)$.
\Cref{eq:depletion-matrix} thus becomes
\begin{equation}
  \label{eq:linear-ode}
  \frac{d\vect{n}}{dt} = \hat{\vect{A}}(t) \vect{n}
\end{equation}
where
\begin{equation}
  \label{eq:linear-interp}
  \hat{\vect{A}}(t) = \left ( 1 - \frac{t}{h} \right) \vect{A}(\vect{n}_i) +
  \frac{t}{h} \vect{A}\left(\vect{n}_{i+1}^p \right).
\end{equation}
We see that $\hat{\vect{A}}$ no longer depends on $\vect{n}$ thereby making
\cref{eq:linear-ode} a linear nonautonomous ODE. Because $\hat{\vect{A}}$ is a
function of time, an approximation is still needed to obtain $\vect{n}_{i+1}$.
The simplest approach~\citep{isotalo2011ane2} is to average
\cref{eq:linear-interp} over the step,
\begin{equation}
  \bar{\vect{A}} = \int_0^h dt \, \hat{\vect{A}}(t) = \frac{\vect{A}(\vect{n}_i)
  + \vect{A}(\vect{n}_{i+1}^p)}{2},
\end{equation}
and then use $\bar{\vect{A}}$ to deplete over the full step:
\begin{equation}
  \vect{n}_{i+1} = \exp \left ( h \bar{\vect{A}} \right ) \vect{n}_i.
\end{equation}
\citet{isotalo2011ane3} suggested an improvement over this approach wherein
$\hat{\vect{A}}$ is averaged over substeps instead of the entire interval. That
is, if we divide the timestep into $m$ substeps, the solution is given by
\begin{equation}
  \begin{split}
    \label{eq:celi-substeps}
    \vect{A}_s &= \int_{(s-1)h/m}^{sh/m} dt \; \hat{\vect{A}}(t), \quad s=1,\dots,m \\
    \vect{n}_{i+1} &= \exp\left(\vect{A}_m \right) \exp \left(\vect{A}_{m-1}\right)
    \cdots \exp\left(\vect{A}_1\right) \vect{n}_i.
  \end{split}
\end{equation}
While using substeps is a reasonable approach for solving \cref{eq:linear-ode},
there are other methods as well. For example, some codes use a backward
differentiation formula rather than a method based on an exponential
integrator~\citep{carpenter2009mc,hykes2017mc,sublet2017nds}. The next section
shows one such example that is used in OpenMC.

@@

\Cref{fig:pwr-keff} shows the difference between $k_\text{eff}$ calculated by
OpenMC and Serpent. The blue points correspond to results using the full
depletion chain, the gray points correspond to points using the reduced chain,
and the orange points correspond to results using the CASL chain. For each
chain, the use of interpolated FPYs is denoted by circles and thermal FPYs by
x's. At zero days, the difference in $k_\text{eff}$ between OpenMC and Serpent
is not statistically significant. As the burnup increases, the difference for
the full chain cases rises to about 20 pcm. The reduced chain case exhibits the
exact same behavior as the full chain as one would expect. Use of the CASL chain
results in a slightly larger difference between OpenMC and Serpent at 50 MWd/kg,
about 40 pcm. We also see that for both the full and CASL chains, changing the
method for handling FPY energy dependence doesn't appear to have much of an
effect on $k_\text{eff}$, which is primarily driven by the prediction of
actinide concentrations.
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr_keff.pdf}
  \caption{Difference in the effective multiplication factor, $k_\text{eff}$,
  between OpenMC and Serpent for the PWR pincell model. While not shown, the one
  standard deviation uncertainty in the difference is about 3.5 pcm.}
  \label{fig:pwr-keff}
\end{figure}

@@

The predicted concentration of fission products depends on both the depletion
chain that is used and the method for handling the energy dependence of the FPY.
We begin with results for the full depletion chain and interpolated FPYs, which
most closely matches the method used in Serpent; \cref{fig:pwr-fp-full-average}
shows the relative difference in fission product concentrations between OpenMC
and Serpent for this case. Most of the differences are less than 0.2\%, and only
a few fission products show differences up to 0.5\%.
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr_fp_full_average.pdf}
  \caption{Relative difference in fission product concentrations between OpenMC
  and Serpent for the PWR pincell model at 5, 12.5, 30, and 50 MWd/kg using the
  full depletion chain and interpolated FPYs in OpenMC.}
  \label{fig:pwr-fp-full-average}
\end{figure}

\Cref{fig:pwr-fp-full-thermal} shows the predicted fission product concentrations
when using the full depletion chain along with thermal FPYs. In this case,
although most fission products are within 1\% of Serpent, they are
systematically overpredicted other than a few nuclides. Because Serpent uses the
average fission energy to interpolate between two sets of FPYs, the systematic
difference is expected when using thermal FPYs in OpenMC. As the incident energy
of a neutron causing fission increases, the ``saddle'' and ``wings'' in the FPY
curve tend to increase significantly, and the peaks around $A=95$ and $A=135$
tend to slightly decrease. This corresponds to exactly what is observed in
\cref{fig:pwr-fp-full-thermal}. Because thermal FPYs were used in OpenMC for
this case, we expect that fission products near one of the two peaks of the FPY
curve will be slightly overpredicted relative to Serpent, and fission products
away from the peak will be underpredicted. This can be confirmed for particular
nuclides. Take, for example, $^{109}$Ag; in the $A=109$ mass chain, the nuclides
with the highest independent yields are $^{109}$Tc and $^{109}$Mo. Both these
nuclides have independent yields that increase significantly with increasing
neutron energy. The same situation occurs for $^{129}$I, whose predominant
precursor is $^{129}$Sn. The independent yields for these three precursor
nuclides are shown in \cref{tab:fp-yields}.
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr_fp_full_thermal.pdf}
  \caption{Relative difference in fission product concentrations between OpenMC
  and Serpent for the PWR pincell model at 5, 12.5, 30, and 50 MWd/kg using the
  full depletion chain and thermal FPYs in OpenMC.}
  \label{fig:pwr-fp-full-thermal}
\end{figure}
\begin{table}[htbp]
  \centering
  \caption{Independent yields of select fission products due to fission in
  $^{235}$U (data from the ENDF/B-VII.1 FPY sublibrary).}
  \label{tab:fp-yields}
  \begin{tabular}{cccc}
    \toprule
    \textbf{Energy Spectrum} & \textbf{$^{109}$Tc} & \textbf{$^{109}$Mo} & \textbf{$^{129}$Sn} \\
    \midrule
    Thermal & 0.00013 & 0.00015 & 0.00230 \\
    Fast & 0.00034 & 0.00042 & 0.00550 \\
    Fusion & 0.00598 & 0.00109 & 0.01162 \\
    \bottomrule
  \end{tabular}
\end{table}

\Cref{fig:pwr-fp-casl-average} shows the relative difference in predicted
fission product concentrations between OpenMC and Serpent when using the CASL
depletion chain and interpolated FPYs. As in \cref{fig:pwr-fp-full-average},
almost all fission products are predicted to well within 1\% at 50 MWd/kg.
However, in this case there is one clear outlier: $^{85}$Kr. Upon further
investigation, it was determined that the root cause for this difference is the
fact that the CASL depletion chain uses a cumulative yield for $^{85}$Kr, and
the cumulative yield of $^{85}$Kr is known to be inconsistent with the
independent yields of the $A=85$ mass chain in
ENDF/B-VII.1~\citep{pigni2015nds}. Serpent relies solely on independent yields
in its depletion solver (as does the full depletion chain). We can conclude,
then, that there is nothing inherently wrong with the CASL depletion chain or
OpenMC; it is simply a matter of the underlying nuclear data being inconsistent.
The 5\% underprediction of $^{85}$Kr is also likely responsible for the slightly
higher difference in $k_\text{eff}$ for the CASL depletion chain shown in
\cref{fig:pwr-keff}.
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr_fp_casl_average.pdf}
  \caption{Relative difference in fission product concentrations between OpenMC
  and Serpent for the PWR pincell model at 5, 12.5, 30, and 50 MWd/kg using the
  CASL depletion chain and interpolated FPYs in OpenMC.}
  \label{fig:pwr-fp-casl-average}
\end{figure}

\Cref{fig:pwr-fp-casl-thermal} shows the relative difference in predicted in
fission product concentrations when using the CASL depletion chain along with
thermal FPYs. The results are quite close to those shown
\cref{fig:pwr-fp-full-thermal}, with the exception of $^{85}$Kr for the
aforementioned reasons.
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr_fp_casl_thermal.pdf}
  \caption{Relative difference in fission product concentrations between OpenMC
  and Serpent for the PWR pincell model at 5, 12.5, 30, and 50 MWd/kg using the
  CASL depletion chain and thermal FPYs in OpenMC.}
  \label{fig:pwr-fp-casl-thermal}
\end{figure}

@@

\Cref{fig:sfr-keff} shows the difference between $k_\text{eff}$ calculated by
OpenMC and Serpent as the assembly is depleted. The blue points correspond to
results using the full depletion chain, and the orange points correspond to
results using the CASL chain. For each chain, simulations with probability
tables on are denoted by circles and simulations without probability tables are
denoted by squares. Unlike in the PWR pincell case, there is a statistically
significant difference in $k_\text{eff}$ at zero days. Let us first consider the
case with probability tables turned off. In this case, $k_\text{eff}$ calculated
by OpenMC is about 20 pcm higher than that of Serpent. When using the full
depletion chain, there is no change in the difference between OpenMC and Serpent
with increasing burnup. When using the CASL depletion chain, the difference
increases by about 20--30 pcm, similar to the behavior shown in
\cref{fig:pwr-keff}. With probability tables turned on, however, the situation
is quite different. At zero days, $k_\text{eff}$ calculated by OpenMC is 20 pcm
lower than the value calculated by Serpent. As the burnup increases, there is an
increasing positive bias between OpenMC and Serpent. To understand the cause of
this difference, it is instructive to look at differences in isotopic
compositions.
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/sfr_keff.pdf}
  \caption{Difference in the effective multiplication factor, $k_\text{eff}$,
  between OpenMC and Serpent for the SFR assembly model. While not shown, the one
  standard deviation uncertainty in the difference is about 3.5 pcm.}
  \label{fig:sfr-keff}
\end{figure}

@@

When comparing results on the SFR assembly model, larger differences in
$k_\text{eff}$ and isotopic concentrations were observed when unresolved
resonance region probability tables were turned on. These differences were found
to be related to how the temperature dependence of cross sections is treated in
the unresolved resonance region. In OpenMC, when the temperature of a material
is between two temperatures at which probability tables are tabulated,
statistical interpolation between the tables is performed. Serpent, on the other
hand, uses probability tables at the lower tabulated temperature. For the SFR
model, this results in lower parasitic neutron absorption in $^{238}$U, lower
production of $^{239}$Pu, and ultimately a lower $k_\text{eff}$. After depleting
for 360 days, there was a 100 pcm difference between OpenMC and Serpent due to
this effect. Although this is not a huge difference, users who are simulating
problems with a non-uniform temperature distribution should be aware of this
behavior. This difference could be mitigated by using nuclear data processed on
a finer temperature grid---in our results, cross sections and probability table
data were being interpolated over a rather large \SI{300}{\kelvin} interval.

@@

While the focus in this work has primarily been on correctness and accuracy, the
performance of a coupled transport--depletion simulation is also an important
consideration that directly impacts usability. The need to determine reaction
rates for hundreds of nuclides leads to a significant performance degredation
during a transport simulation. Research on methods to reduce the computational
expense of obtaining transmutation reaction rates~\citep{salcedoperez2019mc}
show promise but have yet to be incorporated in a release of OpenMC.
